Processing simulation output

### 2020-05-14 results/README.Rmd
update paths

---
title: "Processing simulation output"
output: github_document
---

@@

Create table for manuscript (all means over 15 runs)
```{r}
tabres <- 
  results %>%
  pivot_wider(names_from = dataset, values_from = c("wss.95", "wss.99", "wss.100", "rrf.5", "rrf.10", "rrf.20", "loss"))

>>>>

---
title: "Processing simulation output"
output: github_document
bibliography: ../manuscript/manuscript/asreview.bib
---

@@

Create table for manuscript (all means over 15 runs)
```{r, results = "asis"}
tabres <- 
  results %>%
  pivot_wider(names_from = dataset, values_from = c("wss.95", "wss.99", "wss.100", "rrf.5", "rrf.10", "rrf.20", "loss"))
